Project Protocol

### 2019-10-16 protocol.Rmd
cities and single city dists

#	Title
Assessing the effectiveness of different visualisation methods for Australian spatial data.

@@

This project will test the effectiveness of two types of spatial displays: a choropleth map, and a hexagon map. It will contrast the effectiveness of communicating information when each geographic region is represented by a hexagon, rather than its geographical shape. The purpose of these displays is to convey the spatial distribution of the disease occurrence, or incidence. This can allow for detecting hot spots corresponding to outbreaks, or spatial trends, for example, indicating occurrence is related to latitude or even rural vs urban differences. Effectiveness of the display will be measured by accurate and efficient perception of these patterns.

@@

Participants will pick the map of a true distribution in a line up of null maps more often when the information is presented in a hexagon map, as opposed to a geographic map line up.

@@

1.	Measure the accuracy in spotting a real spatial distribution from a line-up of null maps
2.	Contrast the accuracy when participants pick from geographic or hexagon maps

@@

- Plot type ( Hexagon/ Geographic )
- Spatial dependence structure (Normal errors / Chi-squared errors )

@@

 - Plot type: Geography, Hexagons
 - Error distribution: Normal, Chi-Square
 - Spatial Dependence: Rurality level, North to South, East to West

@@

##	Participant withdrawal
Participants will be able to withdraw by leaving the survey at any time.
XXX will they still be paid?

@@

Information will be collected regarding the design
(including how will you measure, manipulate and/or analyse the information that you collect/gather, matching and sampling strategies, accounting for potential bias, confounding factors and missing information)

>>>>

#	Title
Assessing the effectiveness of visualisation methods for spatial distributions affected by small areas with high population densities.

@@

This project will test the effectiveness of two types of spatial displays: a choropleth map, and a hexagon map. It will contrast the effectiveness of communicating information when each geographic region is represented by a hexagon, rather than its geographical shape. The purpose of these displays is to convey the spatial distribution of the disease occurrence, or incidence. This can allow for detecting hot spots corresponding to outbreaks, or spatial trends, for example, indicating occurrence is related to rural vs urban differences or localised to a single population dense region. Effectiveness of the display will be measured by accurate and efficient detection of these patterns.

@@

When participants see the same data set displayed a line up as a hexagon tile map and geographic map, participants will pick the map that displays a pattern influenced by population density more often when the information is presented in a hexagon tile map.

@@

1.	Measure the accuracy in spotting a real population density related spatial distribution from a line-up of null maps
2.	Contrast the accuracy and efficiency when participants pick from geographic or hexagon maps

@@

- Plot type ( Hexagon / Geographic )
- Spatial dependence structure ( Difference in a single city / Related to population density / North to South )

@@

 - Plot type: Geography, Hexagons
 - Spatial Dependence: Difference in a single city, Related to population density, North to South

@@

##	Participant withdrawal
Participants will be able to withdraw by leaving the survey at any time.

@@
